MATH/COMP 562 ASSIGNMENT 3

### 2023-06-20 assignment-3/article.tex
Remove old title
No need to say "Problem" for every problem
Add problem statements for VC dimension

\title{\normalfont\spacedallcaps{Language reclamation: Literature review}} % The article title

@@

\newenvironment{problem}[2][Problem]
               { \begin{mdframed}[backgroundcolor=gray!20] \textbf{#1 #2} \\}
               {  \end{mdframed}}

@@

\subsection*{Exercise 3.2 (VC dimension of finite hypothesis sets)}
Mohri Exercise 3.14.

\subsection*{Exercise 3.3 (VC dimension of closed balls).}
Mohri Exercise 3.17.

\subsection*{Exercise 3.4 (function class with infinite VC dimension).}
Mohri Exercise 3.20.

>>>>

@@

\newenvironment{problem}[2][]
               { \begin{mdframed}[backgroundcolor=gray!20] \textbf{#1 #2} \\}
               {  \end{mdframed}}

@@

\subsection*{Exercise 3.2 (VC dimension of finite hypothesis sets)}
\begin{problem}{Mohri Exercise 3.14}
VC-dimension of finite hypothesis sets. Show that the VC-dimension of a finite hypothesis set $\mathcal{H}$ is at most $\log_2|\mathcal{H}|$.
\end{problem}

\begin{solution}
Here is a solution
\end{solution}

\subsection*{Exercise 3.3 (VC dimension of closed balls).}
\begin{problem}{Mohri Exercise 3.17}
Show that the VC-dimension of the set of all closed balls in $\mathbb{R}_n$, i.e. sets of the form ${x \in \mathbb{R}_n : kx - x0 k2 \leq r}$ for some $x_0 \in \mathbb{R}_n$ and $r \geq 0$, is less than or equal to $n + 2$.
\end{problem}

\begin{solution}
Here is a solution
\end{solution}

\subsection*{Exercise 3.4 (Function class with infinite VC dimension).}
\begin{problem}{Mohri Exercise 3.20}
Consider the hypothesis family of sine functions: $\{x \to sin(\omega x): \omega \in \mathbb{R}\}$.
\begin{enumerate}[label=(\alph*)]
\item Show that for any $x \in \mathbb{R}$ the points $x$, $2x$, $3x$ and $4x$ cannot be shattered by this family of sine functions.
\item Show that the VC-dimension of the family of sine functions is infinite. (Hint: show that $\{2-i: i \leq m\}$ can be shattered for any $m > 0$.)
\end{enumerate}
\end{problem}

\begin{solution}
Here is a solution
\end{solution}
